NumPy---Array Programming in Python

### 2020-02-05 body.tex
Update references

Two Python array packages existed before NumPy.
The Numeric package began in the mid-90s and provided an array object in
Python, written in C, and linking to standard fast implementations of linear
algebra.
Around 2000, the Space Telescope Science Institute (STScI) software group wrote
a reimplementation of much of Numeric, called NumArray, to support their work
on large memory-mapped arrays and arrays of mixed data type
records \cite{STScI-slither}.
This briefly caused the two communities to diverge, until
2005, when NumPy emerged as a ``best of both worlds'' unification of Numeric
and NumArray \cite{oliphant2006guide}.

>>>>

Two Python array packages existed before NumPy.
The Numeric package began in the mid-90s and provided an array object in
Python, written in C, and linking to standard fast implementations of linear
algebra \cite{Numericmanual}.
Around 2000, the Space Telescope Science Institute (STScI) software group wrote
a reimplementation of much of Numeric, called NumArray, to support their work
on large memory-mapped arrays and arrays of mixed data type
records \cite{greenfield2003numarray}.
This briefly caused the two communities to diverge, until
2005, when NumPy emerged as a ``best of both worlds'' unification of Numeric
and NumArray \cite{oliphant2006guide}.
